Add Amicus Measures

### 2022-04-18 data-cleaning/05-add-amicus-measures.Rmd
add missing brief
update
add vars to shortened amicus text

# data/processed amicus files/amicus_clean_512_no_stride.csv
amicus <- box_read("942789542605")

@@

@@

```{r}
final <- amicus %>% 
  select(case, id, brief, brief_party, forgau:sgauo, text) %>% 
  janitor::clean_names()
```

@@

Missing this brief. I don't see it in Holly's data?

```{r}
amicus %>% filter(id == 861822406799) %>% distinct(brief) %>% pull(brief)
```

@@

```{r}
box_write(final,
           file_name = "amicus_clean_512_no_stride_vars.csv",
           dir_id = 145990409196)
```

>>>>

# data/processed amicus files/amicus_clean_512_no_stride.csv
amicus_party <- box_read("942789542605") %>% select(id, brief_party) %>% distinct(id, brief_party)
# data/processed_amicus_files/amicus_clean_512_no_stride_split.csv
#amicus <- box_read("946701865033")
# data/processed_amicus_files/shortened_amicus_brief_text.csv
amicus <- box_read("910635411098")

@@

If using shortened text file, add in brief_party

```{r}
amicus <- amicus %>% left_join(., amicus_party, by = "id")
```

@@

```{r}
final <- amicus %>% 
  select(case, id, brief, brief_party, forgau:sgauo, text = txt_short) %>% 
  janitor::clean_names()
```

@@

@@

```{r}
box_write(final,
           file_name = "shortened-amicus-text-vars.csv",
           dir_id = 145990409196)
```
